---
title: "API Assignment 4.2"
author: "Brian Waite"
date: "November 4, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#MediaWiki API Experiment

###Student: Brian Waite Date:11/4/2018 Course: Doing Data Science, MSDS 6306


#Introduction

This document is used to demonstrate some of the functionality of the MediaWiki API available in the package WikimediR. The reference manual is available here: <https://cran.r-project.org/web/packages/WikipediR/WikipediR.pdf>

#A category based query into Wikipedia

As a first test, we will try to find pages in a specific category. We'll use "Post-Impressionism" as our search category. 

```{r}
library(WikipediR) #loads the libarary needed
pages = pages_in_category("en","wikipedia",categories="Post-Impressionism") #a function available to search categories
head(pages)
class(pages) 
```

This is a bit messy, so let's see if there are other options.

#Cleaner return data

Fortunately the API Wrapper allows us to add the flag "clean_response = TRUE". This takes the data from a unique data format and converts it to an R data.frame object. 

```{r}
pages = pages_in_category("en","wikipedia",categories="Post-Impressionism", clean_response = TRUE) 
head(pages)
class(pages)  
```

Now we're cooking! 

#Now let's play! 

We can now do easier manipulations to the data, such as: 

Set up a boolean mask to identify the locations of records of interest: 

```{r}
#Set up boolean mask to identify where the record of interest is
mask = pages$title == "Pointillism"
mask
```

Apply those masks to isolate the record of interest: 
```{r}
#Apply boolean mask to obtain record of interest
pageOfInterest = pages[mask,]
pageOfInterest
```

And use that isolated data to get execute additional queries into the API: 

```{r}
#Get Content for pageOfInterest
content = page_content("en","wikipedia",page_name = pageOfInterest$title)
content
```

#What next?

From there we can start to manipulate the content of the page or other information for our intended purpose. But that is a task for another day. 

#Session Information

```{r}
sessionInfo()
```



